### 2022-11-25 doc/manuscript/translocation.qmd
Add exome and Yosemite maps

![Figure SXXXX. Map showing the locations of Bd-naive or recovering frog populations from which DNA samples were collected for the exome capture analyses. To obscure the exact locations of populations, random noise was added to all point coordinates. Black polygons indicate the boundaries of Yosemite, Kings Canyon, and Sequoia national parks (from top to bottom).](figures/map_exome_points.png)

@@

Between 2006 and 2020 we conducted 1-4 translocations of adult frogs to 13 recipient sites (Table S1). In each translocation, adult frogs ($\geq$ 40 mm snout-vent length) were collected from one of three donor populations and measured, weighed, swabbed, and PIT tagged. Frogs were transported to the recipient site either on foot or via helicopter. Following release, translocated populations were visited one to six times per summer (calculate min, max, mean) and assessed using diurnal capture-mark-recapture (CMR) surveys and VES. CMR surveys allowed quantification of adult frog survival, adult population size, and recruitment of new adults, and VES provided estimates of tadpole and subadult abundance.

<!--# Create table of translocation sites, years, frog numbers. Could also create a map if necessary -->

>>>>

![Figure SXXXX. Map showing the locations of Bd-naive or recovering frog populations from which DNA samples were collected for the exome capture analyses. Black polygons indicate the boundaries of Yosemite, Kings Canyon, and Sequoia national parks (from top to bottom). To obscure the exact locations of populations, random noise was added to all point coordinates. Inset map shows the location of the study area with California. In both maps, elevation is indicated with the colored hillshade layer (dark green = lowest elevation, white - highest elevation)](figures/map_exome_points.png)

@@

Between 2006 and 2020 we conducted 1-4 translocations of adult frogs to 12 recipient sites (Table S1, Figure SXXXX). In each translocation, adult frogs ($\geq$ 40 mm snout-vent length) were collected from one of three donor populations and measured, weighed, swabbed, and PIT tagged. Frogs were transported to the recipient site either on foot or via helicopter. Following release, translocated populations were visited one to six times per summer (calculate min, max, mean) and assessed using diurnal capture-mark-recapture (CMR) surveys and VES. CMR surveys allowed quantification of adult frog survival, adult population size, and recruitment of new adults, and VES provided estimates of tadpole and subadult abundance.

<!--# Create table of translocation sites, years, frog numbers. -->

![Figure SXXXX. Map showing the locations of translocated and donor populations in Yosemite National Park (park border indicated by black polygon). To obscure the exact locations of populations, random noise was added to all point coordinates. Elevations are indicated as in Figure SXXXX. See inset map in Figure SXXXX to locate Yosemite National Park within California.](figures/map_translocation_points.png)
